Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Results

\subsection{Context Mapping}
After clones are detected, we map the context of these clones. We have identifier three properties of clones as their context: relation and contents. We identify categories for each of these properties, to get a detailed insight in the context of clones.

@@

\section{Results}

>>>>

\subsection{Context Mapping} \label{sec:context}
After clones are detected, we map the context of these clones. We have identifier three properties of clones as their context: relation and contents. We identify categories for each of these properties, to get a detailed insight in the context of clones.

@@

\section{Results}
In this section we share the results of our experiments.

\subsection{Clone context}
Our initial experiments look into how many clones are found in different contexts (see Sec.~\ref{sec:context}). This results in the Table~\ref{}.
